Visual diagnostics for constrained optimisation with application to guided tours

### 2021-01-03 paper/paper.Rmd
update gridlines for explore_trace_interp()

```{r toy-search, fig.width = 5.5, fig.cap="A comparison of \\code{search\\_better} with different values of the parameter \\code{max\\_tries}. A six-variable dataset \\code{boa6} is used with holes index on a 2D problem. \\code{max\\_tries = 500} allows the optimiser to find better basis with higher index value at iteration six."}
```

@@

```{r toy-interp,fig.width = 5.5, fig.cap = "The resulting trace plot on the interpolated points has been plotted when using three different algorithms to optimise the index. The color represents the number of iteration. It can be observed that each algorithm differs in length in the optimisation and the curvature of the improvement for each algorithm also varies."}
```

>>>>

```{r toy-search, fig.cap="A comparison of \\code{search\\_better} with different values of the parameter \\code{max\\_tries}. A six-variable dataset \\code{boa6} is used with holes index on a 2D problem. \\code{max\\_tries = 500} allows the optimiser to find better basis with higher index value at iteration six."}
```

@@

```{r toy-interp, fig.cap = "The resulting trace plot on the interpolated points has been plotted when using three different algorithms to optimise the index. The color represents the number of iteration. It can be observed that each algorithm differs in length in the optimisation and the curvature of the improvement for each algorithm also varies."}
```
